---
title: "Assignment 4: Cohort Analysis"
author: Jackie Chen
format: html
editor: visual
---

## Instruction

Create a 4 to 6 page Quarto reproducible report, in prose, in a repository on your GitHub account based on the cohort simulated data that contains the following features:

-   introduction section

-   methods section with notation

-   results section with data summary table and at least 2 figures

-   discussion

```{r}
#| label: load-packages
#| include: false
library(tidyverse)
library(dplyr)
library(gtsummary)
library(gt)
```


```{r}
#| label: load-dataset
#| include: false
cohort <- read.csv("cohort.csv")
glimpse(cohort)
```

# Introduction

Briefly explain what this dataset is about and what your analysis aims to show.

# Methods

-   Describe your statistical approach.
-   Include notation if applicable (e.g., $\mu$, $\beta$, etc.).

# Results

## Summary Table

```{r summary-table, message=FALSE, warning=FALSE}
#| label: Summary Table 1
#| warning: false 
#| echo: false 

summary_table <- cohort %>%
  select(smoke, female, age, cardiac, cost) %>%
  mutate(
    smoke = factor(smoke, levels = c(1, 0), labels = c("Yes", "No")),
    female = factor(female, labels = c("No", "Yes")),
    cardiac = factor(cardiac, labels = c("No", "Yes"))
  ) %>%
  tbl_summary(
    by = smoke,
    label = list(
      female ~ "Female",
      age ~ "Age (yrs)",
      cardiac ~ "Cardiac events",
      cost ~ "Medical cost ($USD)"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    missing = "no"
  ) %>%
  add_overall() %>%
  modify_header(label ~ "**Variable**") %>%
  modify_caption("**Table 1. Summary of Participant Characteristics by Smoking Status**") %>%
  bold_labels()

summary_table
```

# Discussion

I

## Disclaimer

I did not use generative AI technology to complete any portion of the work.
